% Sample resume in the v2 (Jake's-Resume) macro style. Used for smoke tests.
\documentclass[letterpaper,11pt]{article}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{fontawesome5}

\newcommand{\resumeItem}[1]{\item\small{{#1}}}
\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}
\newcommand{\achieveRow}[3]{\small\textbf{#1}\ \ \ \ #2 \hfill \textit{\small #3}\\}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

\begin{center}
{\Huge \textbf{Jane Doe}} \\
{\small AI / ML Engineer  -  LLMs, Recommender Systems, MLOps} \\
\href{mailto:jane.doe@example.com}{\faEnvelope\ jane.doe@example.com} \quad
\href{https://linkedin.com/in/janedoe}{\faLinkedin\ linkedin.com/in/janedoe} \quad
\href{https://github.com/janedoe}{\faGithub\ github.com/janedoe}
\end{center}

\section{Professional Summary}
ML engineer with 5 years building production ML systems. Worked on retrieval
and ranking. Used PyTorch and Hugging Face. Helped with MLOps on AWS.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, SQL, Bash} \\
    \textbf{ML \& Deep Learning}{: PyTorch, Hugging Face Transformers, scikit-learn, FAISS, SBERT} \\
    \textbf{LLMs \& GenAI}{: RAG, embeddings, prompt engineering, LangChain} \\
    \textbf{Cloud \& MLOps}{: AWS, EKS, Lambda, S3, Terraform, Docker, FastAPI}
  }}
\end{itemize}

\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Senior ML Engineer}{Aug 2022 -- Present}
    {Acme Search}{Remote}
    \resumeItemListStart
      \resumeItem{Worked on recommendation system using embeddings.}
      \resumeItem{Built RAG pipeline for documentation search.}
      \resumeItem{Helped with MLOps deployment on EKS.}
    \resumeItemListEnd

  \resumeSubheading
    {ML Engineer}{Jul 2019 -- Jul 2022}
    {DataCo}{City, Country}
    \resumeItemListStart
      \resumeItem{Developed churn prediction model in PyTorch.}
      \resumeItem{Productionized model with FastAPI and Docker.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{B.Tech, Computer Science} & \textit{2015 -- 2019} \\
      {\small Some University} & {\small City, Country} \\
    \end{tabular*}
\end{itemize}

\section{Achievements \& Recognition}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item\small{
    \achieveRow{Patent (Granted)}{Indian patent on a search-ranking method}{2023}
    \achieveRow{Best Paper}{Best paper at ConferenceX}{2022}
  }
\end{itemize}

\end{document}
